Fusion Moves for Correlation Clustering

### 2014-11-05 paper/egpaper_for_review.tex
wip

@@

\begin{algorithm}
\begin{scriptsize}
\caption{Fusion Based Algorithms}\label{alg:fusion}

\begin{algorithmic}[1]
\Procedure{Intersection-Based-Inference}{GEN,$J$,$X$}
\State $x^0 \gets \textrm{initial state form } X$
\State $n \gets 0 $                                 \Comment{Number of moves}
\State $m \gets 0 $                                 \Comment{Number of moves without progress}
\While{$m < m_{\max}$ and $n < n_{\max}$ }
\State $n \gets n+1$ 
 \State $x'\gets GEN(x^{n-1},J,X)$                    \Comment{Generate proposal}
 \If{$J(x^{n-1}) \leq J(x')$}                       
   \State $x^{n} \gets Fuse(x^{n-1},x',J)$             
 \Else
   \State $x^{n} \gets Fuse(x',x^{n-1},J)$
 \EndIf
 \If{$J(x^{n}) \leq J(x^{n-1})$}
   \State $m \gets 0$                                 \Comment{Reset counter}
 \Else
   \State $m \gets m+1$                               \Comment{Increment counter}
 \EndIf
\EndWhile
\State \textbf{return} $x^n$
\EndProcedure
\end{algorithmic}
\end{scriptsize}
\end{algorithm}

\begin{algorithm}
\begin{scriptsize}
\caption{Fusion Moves}\label{alg:fusion_moves}
\scriptsize
\begin{algorithmic}[1]
\Require $J(x) \leq J(x')$
\Ensure $J(\hat{x}) \leq J(x)$
\vspace{0.2cm}
\Procedure{Fuse}{$x,x',J$}
\State $\bar{x} \gets \textbf{\scriptsize{Intersect}}(x,x')$  
    \Comment{
        \begin{minipage}{0.4\linewidth} 
            \begin{tiny}
            \begin{singlespace}
                intersect
                uncut edges in $x$ and $x'$,
                return  
                connected component labeling
            \end{singlespace}
            \end{tiny}
        \end{minipage}
    }
\vspace{0.1cm}
\State $ \tilde{G}=(\tilde{E},\tilde{V}),\tilde{W} 
    \gets \textbf{\scriptsize{Contract}}(G,W,\bar{x})$  
    \Comment{ 
        \begin{minipage}{0.2\linewidth} 
            \begin{tiny}
            \begin{singlespace}
                Contract all edges 
                which are uncut in $\bar{x}$ 
            \end{singlespace}
            \end{tiny}
        \end{minipage}
    }
\vspace{0.1cm}
\State $\tilde{x}^*= \argmin\limits_{\tilde{x}} \sum\limits_{e_{ij} \in \tilde{E}} \tilde{w}_{ij}[\tilde{x}_i \neq \tilde{x}_j]$
    \Comment{ 
        \begin{minipage}{0.3\linewidth} 
            \begin{tiny}
            \begin{singlespace}
                Solve the multicut objective
                on smaller graph $\tilde{G}=(\tilde{V},\tilde{E})$
            \end{singlespace}
            \end{tiny}
        \end{minipage}
    }

\State $\hat{x} \gets \textbf{\scriptsize{ProjectBack}}(\tilde{x}^*)$
    \Comment{ 
        \begin{minipage}[\textheight]{0.4\linewidth} 
            \begin{tiny}
            \begin{singlespace}
                Translate the connected component
                labeling $\tilde{x}^*$ of $\tilde{G}$ 
                to a connected component labeling of $G$
            \end{singlespace}
            \end{tiny}
        \end{minipage}
    }
\State \textbf{return} $\hat{x}$
\EndProcedure
\vspace{0.3cm}
\Procedure{FUSE$_{\textrm{BASE}}$}{$x,x',J$}
\State \textbf{return} ${\arg\min}_{\bar{x} \in \{x,x'\}}J(\bar{x})$
\EndProcedure
\end{algorithmic}
\end{scriptsize}
\end{algorithm}

@@

\begin{algorithm}
    \begin{scriptsize}
        \caption{Proposal Generators}\label{alg:proposal_gen}   
        \begin{algorithmic}[1]
            %\Require $J(x) \leq J(x')$
            %\Ensure $J(\hat{x}) \leq J(x)$
            %\vspace{0.3cm}
            \Procedure{Rand2Coloring}{$x,G=(E,V),W$}
            \State $\tilde{W} \gets \textbf{\scriptsize{randomize}}(W) $
            \State $x'= \argmin\limits_{\bar{x}} \sum\limits_{e_{ij} \in E } \tilde{w}_{ij}[\bar{x}_i \neq \bar{x}_j]  [x_i = x_j]   $

            $ \quad\quad s.t.\quad x_i \in \{0, 1\} \forall i $
            \State \textbf{return} $x'$
            \EndProcedure
            %
            %
            \vspace{0.3cm}
            \Procedure{RandEdgeWeightedWatersheds}{$x,G=(E,V),W$}
            \State $\tilde{W} \gets \textbf{\scriptsize{randomize}}(W) $
            \State $ getRandomSeeds$
            \State $ runEdgeWeightedWs$
            \EndProcedure   
            %
            %
            \vspace{0.3cm}
            \Procedure{RandHierarchicalClustering}{$x,G=(E,V),W$}
            \State $\tilde{W} \gets \textbf{\scriptsize{randomize}}(W) $
            \State $\hat{G}=(\hat{E},\hat{V}) \gets G=(E,V)$
            \State $\hat{W} \gets W$
            \While{$|\hat{V}|>\gamma$ \textbf{and}  $\max(\hat{W})>\theta$ }
                \State $\hat{G}=(\hat{E},\hat{V}),\hat{W} \gets 
                    \textbf{\scriptsize{contract}}(\hat{G},\hat{W},  \argmax\limits_{\hat{E}}(\hat{W}) )$
            \EndWhile
            \State $x' \gets \textbf{\scriptsize{getClusterResults}}(???) $ 
            \EndProcedure
        \end{algorithmic}
    \end{scriptsize}
\end{algorithm}

@@

\newpage
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[p]
\centering
\begin{tikzpicture}
\begin{semilogxaxis}[
restrict y to domain=0:4600,
xlabel = {runtime},
xmin = 0,
xmax = 4100,
%ymin =  75282844.25,
%ymax =  81774642.015,
%xtick       = { 1 , 60 , 3600 },
%xticklabels = { 1 sec. , 1 min.  , 1 hour },
%ytick       = {75661636, 78718140, 81774643 },
%yticklabels = {$75661636$, $78718140$, $81774643$ },
width = 0.9\columnwidth,
scaled ticks = false
]
%\addplot[color=black,mark=x] table[x=time,y=HC-CGC]{data/knott-3d-150.data};
%\addlegendentry{HC-CGC}

\addplot[color=red,mark=x] table[x=time,y=CGC-planar]{data/image-seg.data};
\addlegendentry{CGC-planar}

\addplot[color=blue,mark=x] table[x=time, y=MCI-CCIFD]{data/image-seg.data};
\addlegendentry{MCI-CCIFD}

\addplot[color=green,mark=x] table[x=time, y=DYNCC-HC-MC-CGC]{data/image-seg.data};
\addlegendentry{MC-Fusion (HC-MC-CGC)}

\addplot[color=cyan,mark=x] table[x=time, y=DYNCC-HC-CGC-CGC]{data/image-seg.data};
\addlegendentry{MC-Fusion (HC-CGC-CGC)}

\end{semilogxaxis}
\end{tikzpicture}
\caption{image-seg}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[p]
\centering
\begin{tikzpicture}
\begin{semilogxaxis}[
restrict y to domain=-6000:-4500,
xlabel = {runtime},
xmin = 0,
xmax = 4100,
%ymin =  75282844.25,
%ymax =  81774642.015,
%xtick       = { 1 , 60 , 3600 },
%xticklabels = { 1 sec. , 1 min.  , 1 hour },
%ytick       = {75661636, 78718140, 81774643 },
%yticklabels = {$75661636$, $78718140$, $81774643$ },
width = 0.9\columnwidth,
scaled ticks = false
]
%\addplot[color=black,mark=x] table[x=time,y=HC-CGC]{data/knott-3d-150.data};
%\addlegendentry{HC-CGC}

\addplot[color=red,mark=x] table[x=time,y=CGC]{data/knott-3d-150.data};
\addlegendentry{CGC}

\addplot[color=blue,mark=x] table[x=time, y=MCI-CCIFD]{data/knott-3d-150.data};
\addlegendentry{MCI-CCIFD}

\addplot[color=green,mark=x] table[x=time, y=DYNCC-HC-MC-CGC]{data/knott-3d-150.data};
\addlegendentry{MC-Fusion (HC-MC-CGC)}

\addplot[color=cyan,mark=x] table[x=time, y=DYNCC-HC-CGC-CGC]{data/knott-3d-150.data};
\addlegendentry{MC-Fusion (HC-CGC-CGC)}

\end{semilogxaxis}
\end{tikzpicture}
\caption{knott-3d-150}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[p]
\centering
\begin{tikzpicture}
\begin{semilogxaxis}[
restrict y to domain=-40000:-24000,
xlabel = {runtime},
xmin = 0,
xmax = 4100,
%ymin =  75282844.25,
%ymax =  81774642.015,
%xtick       = { 1 , 60 , 3600 },
%xticklabels = { 1 sec. , 1 min.  , 1 hour },
%ytick       = {75661636, 78718140, 81774643 },
%yticklabels = {$75661636$, $78718140$, $81774643$ },
width = 0.9\columnwidth,
scaled ticks = false
]
\addplot[color=black,mark=x] table[x=time,y=HC-CGC]{data/knott-3d-300.data};
\addlegendentry{HC-CGC}

@@

\end{semilogxaxis}
\end{tikzpicture}
\caption{knott-3d-300}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[p]
\centering
\begin{tikzpicture}
\begin{semilogxaxis}[
restrict y to domain=-80000:-60000,
xlabel = {runtime},
xmin = 0,
xmax = 4100,
%ymin =  75282844.25,
%ymax =  81774642.015,
%xtick       = { 1 , 60 , 3600 },
%xticklabels = { 1 sec. , 1 min.  , 1 hour },
%ytick       = {75661636, 78718140, 81774643 },
%yticklabels = {$75661636$, $78718140$, $81774643$ },
width = 0.9\columnwidth,
scaled ticks = false
]
\addplot[color=black,mark=x] table[x=time,y=HC-CGC]{data/knott-3d-450.data};
\addlegendentry{HC-CGC}

\addplot[color=red,mark=x] table[x=time,y=CGC]{data/knott-3d-450.data};
\addlegendentry{CGC}

\addplot[color=blue,mark=x] table[x=time, y=MCI-CCIFD]{data/knott-3d-450.data};
\addlegendentry{MCI-CCIFD}

\addplot[color=green,mark=x] table[x=time, y=DYNCC-HC-MC-CGC]{data/knott-3d-450.data};
\addlegendentry{MC-Fusion (HC-MC-CGC)}

\addplot[color=cyan,mark=x] table[x=time, y=DYNCC-HC-CGC-CGC]{data/knott-3d-450.data};
\addlegendentry{MC-Fusion (HC-CGC-CGC)}

\end{semilogxaxis}
\end{tikzpicture}
\caption{knott-3d-450}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[p]
\centering
\begin{tikzpicture}
\begin{semilogxaxis}[
restrict y to domain=-10000000:-100000,
xlabel = {runtime},
xmin = 0,
xmax = 4100,
%ymin =  75282844.25,
%ymax =  81774642.015,
%xtick       = { 1 , 60 , 3600 },
%xticklabels = { 1 sec. , 1 min.  , 1 hour },
%ytick       = {75661636, 78718140, 81774643 },
%yticklabels = {$75661636$, $78718140$, $81774643$ },
width = 0.9\columnwidth,
scaled ticks = false
]
\addplot[color=black,mark=x] table[x=time,y=HC-CGC]{data/knott-3d-550.data};
\addlegendentry{HC-CGC}

\addplot[color=red,mark=x] table[x=time,y=CGC]{data/knott-3d-550.data};
\addlegendentry{CGC}

\addplot[color=blue,mark=x] table[x=time, y=MCI-CCIFD]{data/knott-3d-550.data};
\addlegendentry{MCI-CCIFD}

\addplot[color=green,mark=x] table[x=time, y=DYNCC-HC-MC-CGC]{data/knott-3d-550.data};
\addlegendentry{MC-Fusion (HC-MC-CGC)}

\addplot[color=cyan,mark=x] table[x=time, y=DYNCC-HC-CGC-CGC]{data/knott-3d-550.data};
\addlegendentry{MC-Fusion (HC-CGC-CGC)}

\end{semilogxaxis}
\end{tikzpicture}
\caption{knott-3d-550}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%\begin{figure}[H]
\begin{figure}[p]
\centering
\begin{tikzpicture}
\begin{semilogxaxis}[
%restrict y to domain=-10000000:-100000,
restrict y to domain=-10000000:700000,
xlabel = {runtime},
xmin = 0,
xmax = 4100,
%ymin =  75282844.25,
%ymax =  81774642.015,
%xtick       = { 1 , 60 , 3600 },
%xticklabels = { 1 sec. , 1 min.  , 1 hour },
%ytick       = {75661636, 78718140, 81774643 },
%yticklabels = {$75661636$, $78718140$, $81774643$ },
width = 0.9\columnwidth,
scaled ticks = false
]
\addplot[color=black,mark=x] table[x=time,y=HC-CGC]{data/seg-3d.data};
\addlegendentry{HC-CGC}

\addplot[color=red,mark=x] table[x=time,y=CGC]{data/seg-3d.data};
\addlegendentry{CGC}

\addplot[color=blue,mark=x] table[x=time, y=MCI-CCIFD]{data/seg-3d.data};
\addlegendentry{MCI-CCIFD}

%\addplot[color=yellow,mark=o] table[x=time, y=DYNCC-HC-MC]{data/seg-3d.data};
%\addlegendentry{MC-Fusion (HC-MC)}

\addplot[color=green,mark=o] table[x=time, y=DYNCC-HC-MC-CGC]{data/seg-3d.data};
\addlegendentry{MC-Fusion (HC-MC-CGC)}

\addplot[color=cyan,mark=x] table[x=time, y=DYNCC-HC-CGC-CGC]{data/seg-3d.data};
\addlegendentry{MC-Fusion (HC-CGC-CGC)}

\end{semilogxaxis}
\end{tikzpicture}
\caption{seg-3d}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

\newcommand{\realplot}[1]{
\begin{tikzpicture}
    \begin{axis}
        \addlegendimage{empty legend}\addlegendentry{Matrix #1}
        \addplot {0};
        \addplot {1};
        \addplot {2};
        \addplot {3};
    \end{axis}
\end{tikzpicture}}

@@

%\begin{algorithm}
%\begin{scriptsize}
%\caption{Fusion Based Algorithms}\label{alg:fusion}
%
%
%
%
%\begin{algorithmic}[1]
%\Procedure{Intersection-Based-Inference}{GEN,$J$,$X$}
%\State $x^0 \gets \textrm{initial state form } X$
%\State $n \gets 0 $                                 \Comment{Number of moves}
%\State $m \gets 0 $                                 \Comment{Number of moves without progress}
%\While{$m < m_{\max}$ and $n < n_{\max}$ }
%\State $n \gets n+1$ 
% \State $x'\gets GEN(x^{n-1},J,X)$                    \Comment{Generate proposal}
% \If{$J(x^{n-1}) \leq J(x')$}                       
%   \State $x^{n} \gets Fuse(x^{n-1},x',J)$             
% \Else
%   \State $x^{n} \gets Fuse(x',x^{n-1},J)$
% \EndIf
% \If{$J(x^{n}) \leq J(x^{n-1})$}
%   \State $m \gets 0$                                 \Comment{Reset counter}
% \Else
%   \State $m \gets m+1$                               \Comment{Increment counter}
% \EndIf
%\EndWhile
%\State \textbf{return} $x^n$
%\EndProcedure
%\end{algorithmic}
%\end{scriptsize}
%\end{algorithm}

%\begin{algorithm}
%\begin{scriptsize}
%\caption{Fusion Moves}\label{alg:fusion_moves}
%\scriptsize
%\begin{algorithmic}[1]
%\Require $J(x) \leq J(x')$
%\Ensure $J(\hat{x}) \leq J(x)$
%\vspace{0.2cm}
%\Procedure{Fuse}{$x,x',J$}
%\State $\bar{x} \gets \textbf{\scriptsize{Intersect}}(x,x')$  
%    \Comment{
%        \begin{minipage}{0.4\linewidth} 
%            \begin{tiny}
%            \begin{singlespace}
%                intersect
%                uncut edges in $x$ and $x'$,
%                return  
%                connected component labeling
%            \end{singlespace}
%            \end{tiny}
%        \end{minipage}
%    }
%\vspace{0.1cm}
%\State $ \tilde{G}=(\tilde{E},\tilde{V}),\tilde{W} 
%    \gets \textbf{\scriptsize{Contract}}(G,W,\bar{x})$  
%    \Comment{ 
%        \begin{minipage}{0.2\linewidth} 
%            \begin{tiny}
%            \begin{singlespace}
%                Contract all edges 
%                which are uncut in $\bar{x}$ 
%            \end{singlespace}
%            \end{tiny}
%        \end{minipage}
%    }
%\vspace{0.1cm}
%\State $\tilde{x}^*= \argmin\limits_{\tilde{x}} \sum\limits_{e_{ij} \in \tilde{E}} \tilde{w}_{ij}[\tilde{x}_i \neq \tilde{x}_j]$
%    \Comment{ 
%        \begin{minipage}{0.3\linewidth} 
%            \begin{tiny}
%            \begin{singlespace}
%                Solve the multicut objective
%                on smaller graph $\tilde{G}=(\tilde{V},\tilde{E})$
%            \end{singlespace}
%            \end{tiny}
%        \end{minipage}
%    }
%
%\State $\hat{x} \gets \textbf{\scriptsize{ProjectBack}}(\tilde{x}^*)$
%    \Comment{ 
%        \begin{minipage}[\textheight]{0.4\linewidth} 
%            \begin{tiny}
%            \begin{singlespace}
%                Translate the connected component
%                labeling $\tilde{x}^*$ of $\tilde{G}$ 
%                to a connected component labeling of $G$
%            \end{singlespace}
%            \end{tiny}
%        \end{minipage}
%    }
%\State \textbf{return} $\hat{x}$
%\EndProcedure
%\vspace{0.3cm}
%\Procedure{FUSE$_{\textrm{BASE}}$}{$x,x',J$}
%\State \textbf{return} ${\arg\min}_{\bar{x} \in \{x,x'\}}J(\bar{x})$
%\EndProcedure
%\end{algorithmic}
%\end{scriptsize}
%\end{algorithm}

@@

%\begin{algorithm}
%    \begin{scriptsize}
%        \caption{Proposal Generators}\label{alg:proposal_gen}   
%        \begin{algorithmic}[1]
%            %\Require $J(x) \leq J(x')$
%            %\Ensure $J(\hat{x}) \leq J(x)$
%            %\vspace{0.3cm}
%            \Procedure{Rand2Coloring}{$x,G=(E,V),W$}
%            \State $\tilde{W} \gets \textbf{\scriptsize{randomize}}(W) $
%            \State $x'= \argmin\limits_{\bar{x}} \sum\limits_{e_{ij} \in E } \tilde{w}_{ij}[\bar{x}_i \neq \bar{x}_j]  [x_i = x_j]   $
%
%            $ \quad\quad s.t.\quad x_i \in \{0, 1\} \forall i $
%            \State \textbf{return} $x'$
%            \EndProcedure
%            %
%            %
%            \vspace{0.3cm}
%            \Procedure{RandEdgeWeightedWatersheds}{$x,G=(E,V),W$}
%            \State $\tilde{W} \gets \textbf{\scriptsize{randomize}}(W) $
%            \State $ getRandomSeeds$
%            \State $ runEdgeWeightedWs$
%            \EndProcedure   
%            %
%            %
%            \vspace{0.3cm}
%            \Procedure{RandHierarchicalClustering}{$x,G=(E,V),W$}
%            \State $\tilde{W} \gets \textbf{\scriptsize{randomize}}(W) $
%            \State $\hat{G}=(\hat{E},\hat{V}) \gets G=(E,V)$
%            \State $\hat{W} \gets W$
%            \While{$|\hat{V}|>\gamma$ \textbf{and}  $\max(\hat{W})>\theta$ }
%                \State $\hat{G}=(\hat{E},\hat{V}),\hat{W} \gets 
%                    \textbf{\scriptsize{contract}}(\hat{G},\hat{W},  \argmax\limits_{\hat{E}}(\hat{W}) )$
%            \EndWhile
%            \State $x' \gets \textbf{\scriptsize{getClusterResults}}(???) $ 
%            \EndProcedure
%        \end{algorithmic}
%    \end{scriptsize}
%\end{algorithm}

@@

\newpage

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\pgfplotsset{every axis legend/.append style={
at={(1.0,1.2)},
anchor=north east}} 
\begin{figure*}
  \begin{subfigure}[b]{0.33\textwidth}
  \centering
  \begin{tikzpicture}
  \begin{semilogxaxis}[
  restrict y to domain=0:4600,
  xlabel = {runtime},
  xmin = 0,
  xmax = 4100,
  %ymin =  75282844.25,
  %ymax =  81774642.015,
  %xtick       = { 1 , 60 , 3600 },
  %xticklabels = { 1 sec. , 1 min.  , 1 hour },
  %ytick       = {75661636, 78718140, 81774643 },
  %yticklabels = {$75661636$, $78718140$, $81774643$ },
  width = 1.0\columnwidth,
  scaled ticks = false,
  ]
  %\addplot[color=black,mark=x] table[x=time,y=HC-CGC]{data/knott-3d-150.data};
  %\addlegendentry{HC-CGC}

  \addplot[color=red,mark=x] table[x=time,y=CGC-planar]{data/image-seg.data};
  %\addlegendentry{CGC-planar}

  \addplot[color=blue,mark=x] table[x=time, y=MCI-CCIFD]{data/image-seg.data};
  %\addlegendentry{MCI-CCIFD}

  \addplot[color=green,mark=x] table[x=time, y=DYNCC-HC-MC-CGC]{data/image-seg.data};
  %\addlegendentry{MC-Fusion (HC-MC-CGC)}

  \addplot[color=cyan,mark=x] table[x=time, y=DYNCC-HC-CGC-CGC]{data/image-seg.data};
  %\addlegendentry{MC-Fusion (HC-CGC-CGC)}

  \end{semilogxaxis}
  \end{tikzpicture}
  \caption{image-seg}
  \end{subfigure}
  \begin{subfigure}[b]{0.33\textwidth}
    \centering
    \begin{tikzpicture}
    \begin{semilogxaxis}[
    restrict y to domain=-6000:-4500,
    xlabel = {runtime},
    xmin = 0,
    xmax = 4100,
    %ymin =  75282844.25,
    %ymax =  81774642.015,
    %xtick       = { 1 , 60 , 3600 },
    %xticklabels = { 1 sec. , 1 min.  , 1 hour },
    %ytick       = {75661636, 78718140, 81774643 },
    %yticklabels = {$75661636$, $78718140$, $81774643$ },
    width = 1.0\columnwidth,
    scaled ticks = false
    ]
    %\addplot[color=black,mark=x] table[x=time,y=HC-CGC]{data/knott-3d-150.data};
    %%\addlegendentry{HC-CGC}
    %
    \addplot[color=red,mark=x] table[x=time,y=CGC]{data/knott-3d-150.data};
    %\addlegendentry{CGC} 
    %
    \addplot[color=blue,mark=x] table[x=time, y=MCI-CCIFD]{data/knott-3d-150.data};
    %\addlegendentry{MCI-CCIFD} 
    %
    \addplot[color=green,mark=x] table[x=time, y=DYNCC-HC-MC-CGC]{data/knott-3d-150.data};
    %\addlegendentry{MC-Fusion (HC-MC-CGC)}
    %
    \addplot[color=cyan,mark=x] table[x=time, y=DYNCC-HC-CGC-CGC]{data/knott-3d-150.data};
    %\addlegendentry{MC-Fusion (HC-CGC-CGC)}
    %
    \end{semilogxaxis}
    \end{tikzpicture}
    \caption{knott-3d-150}
  \end{subfigure}
  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
  \begin{subfigure}[b]{0.33\textwidth}
  \centering
  \begin{tikzpicture}
  \begin{semilogxaxis}[
  restrict y to domain=-40000:-24000,
  xlabel = {runtime},
  xmin = 0,
  xmax = 4100,
  %ymin =  75282844.25,
  %ymax =  81774642.015,
  %xtick       = { 1 , 60 , 3600 },
  %xticklabels = { 1 sec. , 1 min.  , 1 hour },
  %ytick       = {75661636, 78718140, 81774643 },
  %yticklabels = {$75661636$, $78718140$, $81774643$ },
  width = 1.0\columnwidth,
  scaled ticks = false,
  legend to name = named,
  legend columns=5
  ]
  \addplot[color=black,mark=x] table[x=time,y=HC-CGC]{data/knott-3d-300.data};
  \addlegendentry{HC-CGC}

@@

  \end{semilogxaxis}
  \end{tikzpicture}
  \caption{knott-3d-300}
  \end{subfigure}
  \newline
  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
  \begin{subfigure}[b]{0.33\textwidth}
  \centering
  \begin{tikzpicture}
  \begin{semilogxaxis}[
  restrict y to domain=-80000:-60000,
  xlabel = {runtime},
  xmin = 0,
  xmax = 4100,
  %ymin =  75282844.25,
  %ymax =  81774642.015,
  %xtick       = { 1 , 60 , 3600 },
  %xticklabels = { 1 sec. , 1 min.  , 1 hour },
  %ytick       = {75661636, 78718140, 81774643 },
  %yticklabels = {$75661636$, $78718140$, $81774643$ },
  width = 1.0\columnwidth,
  scaled ticks = false
  ]
  \addplot[color=black,mark=x] table[x=time,y=HC-CGC]{data/knott-3d-450.data};
  %\addlegendentry{HC-CGC}

  \addplot[color=red,mark=x] table[x=time,y=CGC]{data/knott-3d-450.data};
  %\addlegendentry{CGC}

  \addplot[color=blue,mark=x] table[x=time, y=MCI-CCIFD]{data/knott-3d-450.data};
  %\addlegendentry{MCI-CCIFD}

  \addplot[color=green,mark=x] table[x=time, y=DYNCC-HC-MC-CGC]{data/knott-3d-450.data};
  %\addlegendentry{MC-Fusion (HC-MC-CGC)}

  \addplot[color=cyan,mark=x] table[x=time, y=DYNCC-HC-CGC-CGC]{data/knott-3d-450.data};
  %\addlegendentry{MC-Fusion (HC-CGC-CGC)}

  \end{semilogxaxis}
  \end{tikzpicture}
  \caption{knott-3d-450}
  \end{subfigure}
  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
  \begin{subfigure}[b]{0.33\textwidth}
  \centering
  \begin{tikzpicture}
  \begin{semilogxaxis}[
  restrict y to domain=-10000000:-100000,
  xlabel = {runtime},
  xmin = 0,
  xmax = 4100,
  %ymin =  75282844.25,
  %ymax =  81774642.015,
  %xtick       = { 1 , 60 , 3600 },
  %xticklabels = { 1 sec. , 1 min.  , 1 hour },
  %ytick       = {75661636, 78718140, 81774643 },
  %yticklabels = {$75661636$, $78718140$, $81774643$ },
  width = 1.0\columnwidth,
  scaled ticks = false
  ]
  \addplot[color=black,mark=x] table[x=time,y=HC-CGC]{data/knott-3d-550.data};
  %\addlegendentry{HC-CGC}

  \addplot[color=red,mark=x] table[x=time,y=CGC]{data/knott-3d-550.data};
  %\addlegendentry{CGC}

  \addplot[color=blue,mark=x] table[x=time, y=MCI-CCIFD]{data/knott-3d-550.data};
  %\addlegendentry{MCI-CCIFD}

  \addplot[color=green,mark=x] table[x=time, y=DYNCC-HC-MC-CGC]{data/knott-3d-550.data};
  %\addlegendentry{MC-Fusion (HC-MC-CGC)}

  \addplot[color=cyan,mark=x] table[x=time, y=DYNCC-HC-CGC-CGC]{data/knott-3d-550.data};
  %\addlegendentry{MC-Fusion (HC-CGC-CGC)}

  \end{semilogxaxis}
  \end{tikzpicture}
  \caption{knott-3d-550}
  \end{subfigure}
  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%\begin{subfigure}[H]
  \begin{subfigure}[b]{0.33\textwidth}
  \centering
  \begin{tikzpicture}
  \begin{semilogxaxis}[
  %restrict y to domain=-10000000:-100000,
  restrict y to domain=-10000000:700000,
  xlabel = {runtime},
  xmin = 0,
  xmax = 4100,
  %ymin =  75282844.25,
  %ymax =  81774642.015,
  %xtick       = { 1 , 60 , 3600 },
  %xticklabels = { 1 sec. , 1 min.  , 1 hour },
  %ytick       = {75661636, 78718140, 81774643 },
  %yticklabels = {$75661636$, $78718140$, $81774643$ },
  width = 1.0\columnwidth,
  scaled ticks = false
  ]
  \addplot[color=black,mark=x] table[x=time,y=HC-CGC]{data/seg-3d.data};
  %\addlegendentry{HC-CGC}

  \addplot[color=red,mark=x] table[x=time,y=CGC]{data/seg-3d.data};
  %\addlegendentry{CGC}

  \addplot[color=blue,mark=x] table[x=time, y=MCI-CCIFD]{data/seg-3d.data};
  %\addlegendentry{MCI-CCIFD}

  %\addplot[color=yellow,mark=o] table[x=time, y=DYNCC-HC-MC]{data/seg-3d.data};
  %%\addlegendentry{MC-Fusion (HC-MC)}

  \addplot[color=green,mark=o] table[x=time, y=DYNCC-HC-MC-CGC]{data/seg-3d.data};
  %\addlegendentry{MC-Fusion (HC-MC-CGC)}
  \addplot[color=cyan,mark=x] table[x=time, y=DYNCC-HC-CGC-CGC]{data/seg-3d.data};
  %DYNCC-HC-CGC-CGC
  %\addlegendentry{MC-Fusion (HC-CGC-CGC)}

  \end{semilogxaxis}
  \end{tikzpicture}
  \caption{seg-3d}
  \end{subfigure}
  \begin{center}
  \hypersetup{linkcolor = black}
  \ref{named}
  \hypersetup{linkcolor = red}
  \end{center}
  \caption{
    Among all tested solvers, the proposed method is the only
    one scaling to large 3D data.
    Except for the small 3D block, CC-Fusion finds very low
    energies one to three magnitudes faster 
    than any other method.
    With increasing block size, is outperformed even more.
    For the 2D datasets CGC is very fast, but our proposed
    solver finds lower energies while still being faster
    than the global optimal multicut solver.
  }
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
